---
title: "Prediction of excercise by machine learning"
author: "Ryota"
date: "10/9/2018"
output: html_document
---

## 1.Overview
One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. Data for the project is from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. The report will indicate to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 

## 2.Analysis
First of all, the tools required are loaded.
```{r}
library(caret)
library(ggplot2)
library(rpart)
library(randomForest)
library(rpart.plot) 
```

Then, the data is loaded for both training and testing. 
```{r}
testing <- read.csv("pml-testing.csv")
training <- read.csv("pml-training.csv")
```

The structure of the training data is checked.
```{r}
str(training)
summary(training$classe)
```
We can see the training data has 19622 observations with 160 variables. And, "classe" variables have five classes: A~E.

Then, in order to eliminate the missing value in the training data, below operations were conducted.
```{r}
training2 <- training[ , colSums(is.na(training)) == 0]
write.csv(training2,file="training2.csv")
training3 = read.csv("training2.csv",header = TRUE,na.strings = c("NA","NaN","","#DIV/0!"))
training4 <- training3[ , colSums(is.na(training3)) == 0]
training4 <- training4[,8:61]
```

The training data is separedted into training and testing part.
```{r}
set.seed(22519) 
inTrain <- createDataPartition(training4$classe, p=0.70, list=F) 
trainData <- training4[inTrain, ] 
testData <- training4[-inTrain, ]
```

Prediction is conducted by the Decision Tree.
```{r}
model_tree <- rpart(classe~.,data=trainData,method="class")
prediction_tree <- predict(model_tree, testData, type="class")
class_tree <- confusionMatrix(prediction_tree, testData$classe) 
class_tree
```
The accuracy was 76.8%.

Then, prediction is tried by the random forest.
```{r}
forest_model <- randomForest(classe ~ ., data=trainData, method="class") 
prediction_forest <- predict(forest_model, testData, type="class") 
random_forest <- confusionMatrix(prediction_forest, testData$classe) 
random_forest
```
The accuracy was 99.6%.

## 3.Conclusion
This report tried to predict the data by using Decision Tree and Random Forest, and indicated that Random Forest was much better (99.6%) than Decesion tree (76.8%), regarding the accuracy.